### 2017-11-14 manuscript.rmd
reset figure numbers in Supplement

```{r preliminaries}

@@

#### Reexamination of pairwise comparisons

@@

@@

The gene trees considered here vary widely in their phylogenetic signal for Tau according to Blomberg's $K$ [@Blomberg:2003jg] (*SI Appendix*, Fig. S2). $K$ describes the tendancy for closely related tips to resemble each other, where $K=0$ indicates that close relatives resemble each other no more than they do distant relatives and $K=1$ indicates that the data have strong phylogenetic signal. To rule out the possibility that gene trees with little phylogenetic signal were diluting support for the Ortholog Conjecture, we removed the `r k_percentile` of genes with the lowest phylogenetic signal, corresponding to a $K$ cutoff for retained genes of greater than `r signif( k_thresh, 3)`. Repeating the phylogenetic analyses on this subset of genes with strongest phylogenetic signal for Tau still do not reject the null hypothesis (Wilcoxon p = $`r  wilcox_test_result_k %>% round( 3 )`$). This indicates that our inability to reject the null hypothesis with phylogenetic methods is not due to a lack of phylogenetic signal.

>>>>

```{r preliminaries, cache=FALSE}

@@

#### Pairwise comparisons oversample lineage-specific changes

@@

\setcounter{figure}{0}
\makeatletter 
\renewcommand{\thefigure}{S\@arabic\c@figure}
\renewcommand{\thetable}{S\@arabic\c@table}
\makeatother

@@

The gene trees considered here vary widely in their phylogenetic signal for Tau according to Blomberg's $K$ [@Blomberg:2003jg] (*SI Appendix*, Fig. S2). $K$ describes the tendancy for closely related tips to resemble each other, where $K=0$ indicates that close relatives resemble each other no more than they do distant relatives and $K=1$ indicates that the data have strong phylogenetic signal. To examine the possibility that gene trees with little phylogenetic signal were diluting support for the Ortholog Conjecture, we removed the `r k_percentile` of genes with the lowest phylogenetic signal, corresponding to a $K$ cutoff for retained genes of greater than `r signif( k_thresh, 3)`. Repeating the phylogenetic analyses on this subset of genes with strongest phylogenetic signal for Tau still do not reject the null hypothesis (Wilcoxon p = $`r  wilcox_test_result_k %>% round( 3 )`$). This indicates that gene trees with little phylogenetic signal are not obscuring support for the Ortholog Conjecture in genes with greater phylogenetic signal.
